Embedding Intuitionistic into Classical Logic

### 2022-07-12 CSL/lipics-v2021-EIICL.tex
Fixed minor errors, removed subsripts

\begin{theorem}
	For every propositional formula $\varphi$ there exists an effective procedure that yields an atom $P$ and a set of $\mathcal S$ of formulas $\psi$ of one of the forms
	$$A_\psi\to (B_\psi\wedge C_\psi), (A_\psi\wedge B_\psi)\to C_\psi, A_\psi\to (B_\psi\vee C_\psi), (A_\psi\vee B_\psi)\to C_\psi, (A_\psi\to B_\psi)\to C_\psi$$for atomic $A_\psi, B_\psi, C_\psi$ such that $\varphi$ is intuitionistically valid if and only if $\bigwedge\mathcal S\to P$ is intuitionistically valid. The size of $\mathcal S$ and time complexity of the transformation are linear in the input size.
\end{theorem}

@@

\begin{theorem}
	Let $\mathcal S$ be as above. Let $\mathcal F_\to\subseteq\mathcal S$ denote formulas $\psi$ of the form $(A_\psi\to B_\psi)\to C_\psi$ and $\Lambda$ denote the set of sequences without repetition over $\mathcal F_\to$. For each atom $A$ and $k\in\Lambda$ consider a new atom $A^k$. Obtain $\mathcal S^\#$ by including formulas as follows
	\begin{itemize}
		\item $A^k\to A^{k\psi}$ for each atom $A$ occurring in $\mathcal S$, $k\in\Lambda$ and $\psi\in\mathcal F_\to$ not occurring in $k$.
		\item $A_\psi^k\to (B_\psi^k\circ C_\psi^k)$ for each $\circ\in\{\wedge,\vee\}$, $A_\psi\to (B_\psi\circ C_\psi)\in\mathcal S$, $k\in\Lambda$.
		\item $(A_\psi^k\circ B_\psi^k)\to C^k$ for each $\circ\in\{\wedge,\vee\}$, $A_\psi\to (B_\psi\circ C_\psi)\in\mathcal S$, $k\in\Lambda$.
		\item $(A^{k\psi}\to B^{k\psi})\to C^k$ for $\psi = (A_\psi\to B_\psi)\to C_\psi\in\mathcal S$, $k\in\Lambda$ if $\psi$ does not occurr in $k$.
	\end{itemize}
	Then $\bigwedge S\to P$ is intuitionistically valid iff $\bigwedge S^\#\to P^\epsilon$ is classically valid, where $\epsilon$ denotes the empty sequence. The size of $\mathcal S^\#$ is in $\mathcal O(|\mathcal S|\cdot2^{|\mathcal F_\to|\cdot\log(|\mathcal F_\to|)})$. Futhermore there is an effective procedure for translating counter-models between the sentences.
\end{theorem}

@@

\begin{theorem}
	For every predicate formula $\varphi$ there exists an effective procedure that yields an atom $P$ and a set $\mathcal S$ of formulas $\psi$ of the forms
	$$\forall \vec z_\psi(A_\psi(\vec a_\psi)\to (B_\psi(\vec b_\psi)\wedge C_\psi(\vec c_\psi))), \forall \vec z_\psi((A_\psi(\vec a_\psi)\wedge B_\psi(\vec b_\psi))\to C_\psi(\vec c_\psi)),$$$$\forall \vec z_\psi(A_\psi(\vec a_\psi)\to (B_\psi(\vec b_\psi)\vee C_\psi(\vec c_\psi))),
	\forall \vec z_\psi((A_\psi(\vec a_\psi)\vee B_\psi(\vec b_\psi))\to C_\psi(\vec c_\psi)),$$$$ \forall \vec z_\psi((A_\psi(\vec a_\psi)\to B_\psi(\vec b_\psi))\to C_\psi(\vec c_\psi)),\forall \vec z_\psi(\forall xA(\vec a_\psi)\to B_\psi(\vec b_\psi)),$$$$ \forall \vec z_\psi(A_\psi(\vec a_\psi)\to\forall xB_\psi(b_\psi)), \forall \vec z_\psi(\exists xA_\psi(\vec a_\psi)\to B_\psi(\vec b_\psi)), \forall \vec z_\psi(A_\psi(\vec a_\psi)\to\exists xB_\psi(b_\psi))$$for atomic $A_\psi, B_\psi, C_\psi$ and vectors of variables $\vec z_\psi, \vec a_\psi, \vec b_\psi, \vec c_\psi$ such that $\varphi$ is intuitionistically valid if and only if $\bigwedge\mathcal S\to P$ is intuitionistically valid. The size of $\mathcal S$ and time complexity of the transformation are linear in the input size.
\end{theorem}

@@

\begin{theorem}\label{fullFOtranslation}
	Let $\mathcal S$ be as above and $\mathcal F_\to\subseteq\mathcal S$ contain formulas of the form $\forall \vec t((A(\vec z_A)\to B(\vec z_B))\to C(\vec z_C))$ and $\mathcal F_\forall\subseteq\mathcal S$ the formulas of the form $\forall \vec z(\forall xA(\vec z_A)\to B(\vec z_B))$. Let $\mathcal F = \mathcal F_\to\cup\mathcal F_\forall$. For every $n$-ary atomic relation $R$ define a new $n+1$-ary relation $R^\#$. For every $\psi\in\mathcal F$ define a new function symbol $f_\psi$. Consider a new binary relation symbol $E$ and define $\vec E(\vec x, u) := \bigwedge\{E(x, u)\:|\:x\in\vec x\}$. Obtain $\mathcal S^\#$ by including formulas as follows:
	\begin{itemize}
		\item $\forall \vec z_\psi\forall u(\vec E(\vec z_\psi, u)\to (A_\psi^\#(\vec a_\psi, u)\to (B_\psi^\#(\vec b_\psi, u)\circ C_\psi^\#(\vec c_\psi, u))))$\\for each $\circ\in\{\wedge, \vee\}, \psi = \forall \vec z_\psi(A_\psi(\vec a_\psi)\to (B_\psi(\vec b_\psi)\circ C_\psi(\vec c_\psi)))\in\mathcal S$
		\item $\forall \vec z_\psi\forall u(\vec E(\vec z_\psi, u)\to (A_\psi^\#(\vec a_\psi, u)\circ B_\psi^\#(\vec b_\psi, u))\to C_\psi^\#(\vec c_\psi, u))$\\for each $\circ\in\{\wedge, \vee\}, \psi = \forall \vec z_\psi((A_\psi(\vec a_\psi)\circ B_\psi(\vec b_\psi))\to C_\psi(\vec c_\psi))\in\mathcal S$
		\item $\forall \vec z_\psi\forall u(\vec E(\vec z_\psi, u)\to(A_\psi^\#(\vec a_\psi, f_\psi(\vec z_\psi, u))\to B_\psi^\#(\vec b_\psi, f_\psi(\vec z_\psi, u)))\to C_\psi^\#(\vec c_\psi, u))$ for each $\psi = \forall \vec z_\psi((A_\psi(\vec a_\psi)\to B_\psi(\vec b_\psi))\to C_\psi(\vec c_\psi))\in\mathcal S$
		\item  $\forall \vec z_\psi\forall u(\vec E(\vec z_\psi, u)\to \forall x(E(x, f_\psi(\vec z_\psi, u))\to A_\psi^\#(\vec a_\psi, f_\psi(\vec z_\psi, u)))\to B^\#(\vec b_\psi, u))$\\for each $\forall \vec z_\psi(\forall xA_\psi(\vec a_\psi)\to B_\psi(\vec t_B))\in\mathcal S$.
		\item $\forall \vec z_\psi\forall u(\vec E(\vec z_\psi, u)\to A^\#_\psi(\vec a_\psi, u)\to \forall x(E(x, u)\to B^\#_\psi(\vec b_\psi, u)))$\\for each $\forall \vec t(A_\psi(\vec a_\psi)\to \forall xB_\psi(\vec b_\psi))\in\mathcal S$.
		\item $\forall \vec z_\psi\forall u(\vec E(\vec z_\psi, u)\to \exists x(E(x, u)\wedge A^\#_\psi(\vec z_\psi, u))\to B^\#_\psi(\vec b_\psi))$\\for each $\forall \vec z_\psi(\exists xA_\psi(\vec a_\psi)\to B_\psi(\vec b_\psi))\in\mathcal S$
		\item $\forall \vec z_\psi\forall u(\vec E(\vec z_\psi, u)\to A^\#_\psi(\vec b_\psi)\to \exists x(E(x, u)\wedge B^\#_\psi(\vec b_\psi, u)))$\\for each $\forall \vec z_\psi(A_\psi(\vec a_\psi)\to \exists xB_\psi(\vec b_\psi))\in\mathcal S$
	\end{itemize}
	Then $\bigwedge S\to P$ is intuitionistically iff $\exists xE(x, s)\to K\to \bigwedge\mathcal S^\#\to P^\#(s)$ is classically valid, where $s$ is a new constant symbol, $\Sigma$ is the original signature and
	\begin{align*}
		K := &\:\bigwedge\{\forall x\forall u((E(x, u)\to E(x, f_\psi(u)))\:|\:\psi\in\mathcal F\}\wedge\\
		&\:\forall u\left(\exists xE(x, u)\to \bigwedge\{\forall\vec z(\vec E(\vec z, u)\to E(f(\vec z), u))\:|\:\text{$f$ is a function symbol in $\Sigma$}\}\right)\wedge\\
		&\:\bigwedge\{\forall\vec z_1\forall \vec z_2\forall u(A^\#(\vec z_1, u)\to A^\#(\vec z_1, f_\psi(\vec z_2, u)))\:|\:\text{$\psi\in\mathcal F$, $A$ is a relation symbol in $\Sigma$}\}
	\end{align*}
	The size of the obtained formula is linear in the input. However a $|\mathcal F| + 1$ new function symbols and the new binary predicate $E$ were introduced and each $n$-ary relation symbol has been extended to a $n+1$-ary relation symbol.
\end{theorem}

@@

\begin{definition}
	For formulas $\varphi$ we define the Skolemization $\varphi^S_T$ and Herbrandization $\varphi^H_T$ with respect to $T$ by simultaneous induction as follows:
	\begin{itemize}
		\item $A^S_T = A^H_T = A$ for each atomic $A$.
		\item $(\varphi\circ\psi)^X_T = \varphi^X_T\circ\psi^X_T$ for $\circ\in\{\wedge, \vee\}$, $X\in\{S, H\}$.
		\item $(\varphi\to\psi)^S_T = \varphi^H_T\to \psi^S_T$\\$(\varphi\to\psi)^H_T = \varphi^S_T\to\psi^H_T$.
		\item $(\forall x\varphi)^S_T = \forall x(\varphi[a/x]^S_{T\cup\{a\}}[x/a])$ where $a$ is a new free variable\\$(\forall x\varphi)^H_T = \varphi[s(t_1,\dots,t_n)/x]^H_T$ where $s$ is a new function, $\{t_1\dots t_n\} = T$.
		\item $(\exists x\varphi)^S_T = \varphi[s(t_1,\dots,t_n)/x]^S_T$ where $s$ is a new function, $\{t_1\dots t_n\} = T$\\$(\exists x\varphi)^H_T = \exists x(\varphi[a/x]^H_{T\cup\{a\}}[x/a])$ where $a$ is a new free variable.
	\end{itemize}
	Let $\varphi^S = (\exists x_1\dots\exists x_n \varphi[x_1/a_1\dots x_n/a_n])^S_\emptyset$ and $\varphi^H = (\exists x_1\dots\exists x_n \varphi[x_1/a_1\dots x_n/a_n])^H_\emptyset$ where $a_1,\dots,a_n$ are the free variables occurring in $\varphi$.
\end{definition}

@@

\begin{definition}
	Let $\varphi$ be a propositional formula. Define $\varphi^{u}$ inductively as follows:
	\begin{itemize}
		\item $A^{u} = A(u)$ for every propositional variable $A$.
		\item $(\varphi\circ\psi)^u = \varphi^u\circ\psi^u$ for $\circ\in\{\wedge, \vee\}$.
		\item $(\varphi\to \psi)^u = \forall w(u\preceq w\to\varphi^{w}\to\psi^{w})$ where $w$ is some new variable.
	\end{itemize}
	Let $K(\varphi)$ encode the Kripke semantics, i.e.
	$$K(\varphi) = \text{PartialOrder}(\preceq)\wedge\forall u\forall w(u\preceq w\to \text{Persistent}(u, w))$$
	with e.g.
	\begin{align*}
		\text{PartialOrder}(\preceq) =&\:\forall u(u\preceq u)\wedge\forall u\forall w(u\preceq w\to w\preceq u\to u = w)\wedge\\&\:\forall u\forall v\forall w(u\preceq v\to v\preceq w\to u\preceq w)\\
		Persistent(u, w)=&\:\bigwedge \{A(u)\to A(w))\:|\: \text{ $A$ is a propositional variable that occurs in $\varphi$}\}
	\end{align*}
	Then define
	$$\varphi^{C} = K(\varphi)\to \varphi^{u}$$
	where $u$ is some free variable.
\end{definition}

@@

\begin{example}
	Consider the law of excluded middle $$\varphi = (A\to \bot)\vee A$$ which is not intuitionistically valid. Then
	\begin{align*}
		\varphi^{C} &= K(\varphi)\to ((A\to \bot)\vee A)^u\\
		&= K(\varphi)\to (A\to \bot)^u\vee A^u\\
		&= K(\varphi)\to (\forall u'( u\preceq u' \to A^{u'}\to \bot^{u'})\vee A(u))\\
		&= K(\varphi)\to (\forall u' (u\preceq u' \to A(u')\to \bot(u'))\vee A(u))
	\end{align*}
	and indeed $\varphi^{C}$ admits a counter model with domain $\{u, u'\}$ where $u \preceq u'$, $A(u) = 0, A(u') = 1$.
\end{example}

@@

\begin{definition}
	Let $\varphi$ be some formula. For each sub(semi)formula $\psi$ of $\varphi$ consider some new $n$-ary relation symbol $P_\psi$ where $n$ is the number of variables occurring in $\psi$ that is not quantified within $\psi$. We denote those variables with $\vec t_\psi$ in some arbitrary but fixed order. We inductively define clause sets $\mathcal S^+(\varphi)$ and $\mathcal S^-(\varphi)$ as follows:
	\begin{itemize}
		\item For every atomic formula $A$\\$\mathcal S^+(A) = \{P_A(\vec t_A)\to A\}$\\$\mathcal S^-(A) = \{A\to P_A(\vec t_A)\}$
		\item For every conjunction or disjunction $\varphi\circ\psi$ with $\circ\in\{\wedge,\vee\}$\\$\mathcal S^+(\varphi\circ\psi) = \{P_{\varphi\circ\psi}(\vec t_{\varphi\circ\psi})\to P_{\varphi}(\vec t_\varphi)\circ P_{\psi}(\vec t_\psi)\}\cup \mathcal S^+(\varphi)\cup \mathcal S^+(\psi)$\\$\mathcal S^-(\varphi\circ\psi) =\{P_{\varphi}(\vec t_\varphi)\circ P_{\psi}(\vec t_\psi)\to P_{\varphi\circ\psi}(\vec t_{\varphi\circ\psi})\}\cup \mathcal S^-(\varphi)\cup \mathcal S^-(\psi)$
		\item For every implication $\varphi \to\psi$\\$\mathcal S^+(\varphi\to\psi) = \{(P_{\varphi\to\psi}(\vec t_{\varphi\to\psi})\wedge P_{\varphi}(\vec t_\varphi))\to P_{\psi}(\vec t_\psi)\}\cup \mathcal S^-(\varphi)\cup \mathcal S^+(\psi)$\\$\mathcal S^-(\varphi\to\psi)  = \{(P_{\varphi}(\vec t_\varphi)\to P_{\psi}(\vec t_\psi))\to P_{\varphi\to\psi}(\vec t_{\varphi\to\psi})\}\cup \mathcal S^+(\varphi)\cup \mathcal S^-(\varphi)$
		\item For quantified formulas $Qx\varphi(x)$ with $Q\in \{\forall,\exists\}$\\$\mathcal S^+(Qx\varphi(x)) = \{P_{Qx\varphi}(\vec t_{Qx\varphi})\to QxP_{\varphi}(\vec t_{\varphi})\}\cup \{\forall x\psi\:|\:\psi\in\mathcal S^+(\varphi)\}$\\$\mathcal S^-(Qx\varphi(x))  = \{QxP_{\varphi}(\vec t_{\varphi})\to P_{Qx\varphi}(\vec t_{Qx\varphi})\}\cup \{\forall x\psi\:|\:\psi\in\mathcal S^-(\varphi)\}$
	\end{itemize}
	and have $\mathcal S(\varphi) = \mathcal S^+(\varphi)\cup\mathcal S^-(\varphi)$.
\end{definition}

@@

\begin{definition}
	For every classical and intuitionistic structure $\mathcal M$ define a structure $\mathcal S(\mathcal M,\varphi)$ that agrees with $\mathcal M$ on everything except the interpretation(s) of atoms $P_\psi$. By slight abuse of notation we denote with $\vec t_\psi$ elements of the domain instead of variables. In the classical case have	
	$$P_{\varphi\wedge\psi}^I(\vec t_{\varphi\wedge\psi}) \Leftrightarrow P_{\varphi}^I(\vec t_\varphi)\wedge P_{\psi}^I(\vec t_\psi)\indent P_{\varphi\vee\psi}^I(\vec t_{\varphi\vee\psi}) \Leftrightarrow P_{\varphi}^I(\vec t_\varphi)\vee P_{\psi}^I((\vec t_\psi))$$$$ P_{\varphi\to\psi}^I(\vec t_{\varphi\to\psi}) \Leftrightarrow (\neg P_{\varphi}^I(\vec t_{\varphi}))\vee P_{\psi}^I(\vec t_{\psi})$$
	$$P_{\forall x\varphi}^I(\vec t_{\forall x\varphi}) \Leftrightarrow \{\vec t\:|\:\:P_{\varphi}^I(\vec t_\varphi) \text{ for all $x\in M$}\}$$$$ P_{\exists x\varphi}^I(\vec t_{\exists x\varphi}) \Leftrightarrow \{\vec t\:|\:\:P_{\varphi}^I(\vec t_\varphi) \text{ for some $x\in M$}\}$$
	\\

>>>>

\begin{theorem}
	For every propositional formula $\varphi$ there exists an effective procedure that yields an atom $P$ and a set of $\mathcal S$ of formulas  of one of the forms
	$$A\to (B\wedge C), (A\wedge B)\to C, A\to (B\vee C), (A\vee B)\to C, (A\to B)\to C$$for atomic $A, B, C$ such that $\varphi$ is intuitionistically valid if and only if $\bigwedge\mathcal S\to P$ is intuitionistically valid. The size of $\mathcal S$ and time complexity of the transformation are linear in the input size.
\end{theorem}

@@

\begin{theorem}
	Let $\mathcal S$ be as above. Let $\mathcal F_\to\subseteq\mathcal S$ denote formulas $\psi$ of the form $(A_\psi\to B_\psi)\to C_\psi$ and $\Lambda$ denote the set of sequences without repetition over $\mathcal F_\to$. For each atom $A$ and $k\in\Lambda$ consider a new atom $A^k$. Obtain $\mathcal S^\#$ by including formulas as follows
	\begin{itemize}
		\item $A^k\to A^{k\psi}$ for each atom $A$ occurring in $\mathcal S$, $k\in\Lambda$ and $\psi\in\mathcal F_\to$ not occurring in $k$.
		\item $A^k\to (B^k\circ C^k)$ for each $\circ\in\{\wedge,\vee\}$, $A\to (B\circ C)\in\mathcal S$, $k\in\Lambda$.
		\item $(A^k\circ B^k)\to C^k$ for each $\circ\in\{\wedge,\vee\}$, $A\to (B\circ C)\in\mathcal S$, $k\in\Lambda$.
		\item $(A^{k\psi}\to B^{k\psi})\to C^k$ for $\psi = (A\to B)\to C\in\mathcal S$, $k\in\Lambda$ if $\psi$ does not occurr in $k$.
	\end{itemize}
	Then $\bigwedge S\to P$ is intuitionistically valid iff $\bigwedge S^\#\to P^\epsilon$ is classically valid, where $\epsilon$ denotes the empty sequence. The size of $\mathcal S^\#$ is in $\mathcal O(|\mathcal S|\cdot2^{|\mathcal F_\to|\cdot\log(|\mathcal F_\to|)})$. Futhermore there is an effective procedure for translating counter-models between the sentences.
\end{theorem}

@@

\begin{theorem}
	For every predicate formula $\varphi$ there exists an effective procedure that yields an atom $P$ and a set $\mathcal S$ of formulas of the forms
	$$\forall \vec z(A(\vec a)\to (B(\vec b)\wedge C(\vec c))), \forall \vec z((A(\vec a)\wedge B(\vec b))\to C(\vec c)),$$$$\forall \vec z(A(\vec a)\to (B(\vec b)\vee C(\vec c))),
	\forall \vec z((A(\vec a)\vee B(\vec b))\to C(\vec c)),$$$$ \forall \vec z((A(\vec a)\to B(\vec b))\to C(\vec c)),\forall \vec z(\forall xA(\vec a)\to B(\vec b)),$$$$ \forall \vec z(A(\vec a)\to\forall xB(b)), \forall \vec z(\exists xA(\vec a)\to B(\vec b)), \forall \vec z(A(\vec a)\to\exists xB(b))$$for atomic $A, B, C$ and vectors of variables $\vec z, \vec a, \vec b, \vec c$ such that $\varphi$ is intuitionistically valid if and only if $\bigwedge\mathcal S\to P$ is intuitionistically valid. The size of $\mathcal S$ and time complexity of the transformation are linear in the input size.
\end{theorem}

@@

\begin{theorem}\label{fullFOtranslation}
	Let $\mathcal S$ be as above and $\mathcal F_\to\subseteq\mathcal S$ contain formulas of the form $\forall \vec t((A(\vec z_A)\to B(\vec z_B))\to C(\vec z_C))$ and $\mathcal F_\forall\subseteq\mathcal S$ the formulas of the form $\forall \vec z(\forall xA(\vec z_A)\to B(\vec z_B))$. Let $\mathcal F = \mathcal F_\to\cup\mathcal F_\forall$. For every $n$-ary atomic relation $R$ define a new $n+1$-ary relation $R^\#$. For every $\psi\in\mathcal F$ define a new function symbol $f_\psi$. Consider a new binary relation symbol $E$ and define $\vec E(\vec x, u) := \bigwedge\{E(x, u)\:|\:x\in\vec x\}$. Obtain $\mathcal S^\#$ by including formulas as follows:
	\begin{itemize}
		\item $\forall \vec z\forall u(\vec E(\vec z, u)\to (A^\#(\vec a, u)\to (B^\#(\vec b, u)\circ C^\#(\vec c, u))))$\\for each $\circ\in\{\wedge, \vee\}, \psi = \forall \vec z(A(\vec a)\to (B(\vec b)\circ C(\vec c)))\in\mathcal S$
		\item $\forall \vec z\forall u(\vec E(\vec z, u)\to (A^\#(\vec a, u)\circ B^\#(\vec b, u))\to C^\#(\vec c, u))$\\for each $\circ\in\{\wedge, \vee\}, \psi = \forall \vec z((A(\vec a)\circ B(\vec b))\to C(\vec c))\in\mathcal S$
		\item $\forall \vec z\forall u(\vec E(\vec z, u)\to(A^\#(\vec a, f(\vec z, u))\to B^\#(\vec b, f(\vec z, u)))\to C^\#(\vec c, u))$ for each $\psi = \forall \vec z((A(\vec a)\to B(\vec b))\to C(\vec c))\in\mathcal S$
		\item  $\forall \vec z\forall u(\vec E(\vec z, u)\to \forall x(E(x, f(\vec z, u))\to A^\#(\vec a, f(\vec z, u)))\to B^\#(\vec b, u))$\\for each $\forall \vec z(\forall xA(\vec a)\to B(\vec t_B))\in\mathcal S$.
		\item $\forall \vec z\forall u(\vec E(\vec z, u)\to A^\#(\vec a, u)\to \forall x(E(x, u)\to B^\#(\vec b, u)))$\\for each $\forall \vec t(A(\vec a)\to \forall xB(\vec b))\in\mathcal S$.
		\item $\forall \vec z\forall u(\vec E(\vec z, u)\to \exists x(E(x, u)\wedge A^\#(\vec z, u))\to B^\#(\vec b))$\\for each $\forall \vec z(\exists xA(\vec a)\to B(\vec b))\in\mathcal S$
		\item $\forall \vec z\forall u(\vec E(\vec z, u)\to A^\#(\vec b)\to \exists x(E(x, u)\wedge B^\#(\vec b, u)))$\\for each $\forall \vec z(A(\vec a)\to \exists xB(\vec b))\in\mathcal S$
	\end{itemize}
	Then $\bigwedge S\to P$ is intuitionistically iff $\exists xE(x, s)\to K\to \bigwedge\mathcal S^\#\to P^\#(s)$ is classically valid, where $s$ is a new constant symbol, $\Sigma$ is the original signature and
	\begin{align*}
		K := &\:\bigwedge\{\forall x\forall u((E(x, u)\to E(x, f_\psi(u)))\:|\:\psi\in\mathcal F\}\wedge\\
		&\:\forall u\left(\exists xE(x, u)\to \bigwedge\{\forall\vec z(\vec E(\vec z, u)\to E(f(\vec z), u))\:|\:\text{$f$ is a function symbol in $\Sigma$}\}\right)\wedge\\
		&\:\bigwedge\{\forall\vec z_1\forall \vec z_2\forall u(A^\#(\vec z_1, u)\to A^\#(\vec z_1, f_\psi(\vec z_2, u)))\:|\:\text{$\psi\in\mathcal F$, $A$ is a relation symbol in $\Sigma$}\}
	\end{align*}
	The size of the obtained formula is linear in the input. However a $|\mathcal F| + 1$ new function symbols and the new binary predicate $E$ were introduced and each $n$-ary relation symbol has been extended to a $n+1$-ary relation symbol.
\end{theorem}

@@

\begin{definition}
	For formulas $\varphi$ we define the Skolemization $\varphi^S_Z$ and Herbrandization $\varphi^H_Z$ with respect to $Z$ by simultaneous induction as follows:
	\begin{itemize}
		\item $A^S_T = A^H_Z = A$ for each atomic $A$.
		\item $(\varphi\circ\psi)^X_Z = \varphi^X_Z\circ\psi^X_Z$ for $\circ\in\{\wedge, \vee\}$, $X\in\{S, H\}$.
		\item $(\varphi\to\psi)^S_Z = \varphi^H_Z\to \psi^S_Z$\\$(\varphi\to\psi)^H_Z = \varphi^S_Z\to\psi^H_Z$.
		\item $(\forall x\varphi)^S_Z = \forall x(\varphi[a/x]^S_{T\cup\{a\}}[x/a])$ where $a$ is a new free variable\\$(\forall x\varphi)^H_Z = \varphi[s(z_1,\dots,z_n)/x]^H_Z$ where $s$ is a new function, $\{z_1\dots z_n\} = Z$.
		\item $(\exists x\varphi)^S_Z = \varphi[s(z_1,\dots,z_n)/x]^S_Z$ where $s$ is a new function, $\{z_1\dots z_n\} = Z$\\$(\exists x\varphi)^H_Z = \exists x(\varphi[a/x]^H_{Z\cup\{a\}}[x/a])$ where $a$ is a new free variable.
	\end{itemize}
	Let $\varphi^S = (\exists x_1\dots\exists x_n \varphi[x_1/a_1\dots x_n/a_n])^S_\emptyset$ and $\varphi^H = (\forall x_1\dots\forall x_n \varphi[x_1/a_1\dots x_n/a_n])^H_\emptyset$ where $a_1,\dots,a_n$ are the free variables occurring in $\varphi$.
\end{definition}

@@

\begin{definition}
	Let $\varphi$ be a propositional formula. Define $\varphi^{u}$ inductively as follows:
	\begin{itemize}
		\item $A^{u} = A(u)$ for every propositional variable $A$.
		\item $\bot^u = \bot$.
		\item $(\varphi\circ\psi)^u = \varphi^u\circ\psi^u$ for $\circ\in\{\wedge, \vee\}$.
		\item $(\varphi\to \psi)^u = \forall w(u\preceq w\to\varphi^{w}\to\psi^{w})$ where $w$ is some new variable.
	\end{itemize}
	Let $K(\varphi)$ encode the Kripke semantics, i.e.
	$$K(\varphi) = \text{\normalfont PartialOrder}(\preceq)\wedge\forall u\forall w(u\preceq w\to \text{\normalfont Persistent}(u, w))$$
	with e.g.
	\begin{align*}
		\text{\normalfont PartialOrder}(\preceq) =&\:\forall u(u\preceq u)\wedge\forall u\forall w(u\preceq w\to w\preceq u\to u = w)\wedge\\&\:\forall u\forall v\forall w(u\preceq v\to v\preceq w\to u\preceq w)\\
		\text{\normalfont Persistent}(u, w)=&\:\bigwedge \{A(u)\to A(w))\:|\: \text{ $A$ is a propositional variable that occurs in $\varphi$}\}
	\end{align*}
	Then define
	$$\varphi^{C} = K(\varphi)\to \varphi^{u}$$
	where $u$ is some free variable.
\end{definition}

@@

\begin{example}
	Consider the law of excluded middle $$\varphi = (A\to \bot)\vee A$$ which is not intuitionistically valid. Then
	\begin{align*}
		\varphi^{C} &= K(\varphi)\to ((A\to \bot)\vee A)^u\\
		&= K(\varphi)\to (A\to \bot)^u\vee A^u\\
		&= K(\varphi)\to (\forall u'( u\preceq u' \to A^{u'}\to \bot^{u'})\vee A(u))\\
		&= K(\varphi)\to (\forall u' (u\preceq u' \to A(u')\to \bot)\vee A(u))
	\end{align*}
	and indeed $\varphi^{C}$ admits a counter model with domain $\{u, u'\}$ where $u \preceq u'$, $A(u) = 0, A(u') = 1$.
\end{example}

@@

\begin{definition}
	Let $\varphi$ be some formula. For each sub(semi)formula $\psi$ of $\varphi$ consider some new $n$-ary relation symbol $P_\psi$ where $n$ is the number of variables occurring in $\psi$ that is not quantified within $\psi$. We denote those variables with $\vec z_\psi$ in some arbitrary but fixed order. We inductively define clause sets $\mathcal S^+(\varphi)$ and $\mathcal S^-(\varphi)$ as follows:
	\begin{itemize}
		\item For every atomic formula $A$\\$\mathcal S^+(A) = \{P_A(\vec z_A)\to A\}$\\$\mathcal S^-(A) = \{A\to P_A(\vec z_A)\}$
		\item For every conjunction or disjunction $\varphi\circ\psi$ with $\circ\in\{\wedge,\vee\}$\\$\mathcal S^+(\varphi\circ\psi) = \{P_{\varphi\circ\psi}(\vec z_{\varphi\circ\psi})\to P_{\varphi}(\vec z_\varphi)\circ P_{\psi}(\vec z_\psi)\}\cup \mathcal S^+(\varphi)\cup \mathcal S^+(\psi)$\\$\mathcal S^-(\varphi\circ\psi) =\{P_{\varphi}(\vec z_\varphi)\circ P_{\psi}(\vec z_\psi)\to P_{\varphi\circ\psi}(\vec z_{\varphi\circ\psi})\}\cup \mathcal S^-(\varphi)\cup \mathcal S^-(\psi)$
		\item For every implication $\varphi \to\psi$\\$\mathcal S^+(\varphi\to\psi) = \{(P_{\varphi\to\psi}(\vec z_{\varphi\to\psi})\wedge P_{\varphi}(\vec z_\varphi))\to P_{\psi}(\vec z_\psi)\}\cup \mathcal S^-(\varphi)\cup \mathcal S^+(\psi)$\\$\mathcal S^-(\varphi\to\psi)  = \{(P_{\varphi}(\vec z_\varphi)\to P_{\psi}(\vec z_\psi))\to P_{\varphi\to\psi}(\vec z_{\varphi\to\psi})\}\cup \mathcal S^+(\varphi)\cup \mathcal S^-(\psi)$
		\item For quantified formulas $Qx\varphi(x)$ with $Q\in \{\forall,\exists\}$\\$\mathcal S^+(Qx\varphi(x)) = \{P_{Qx\varphi}(\vec z_{Qx\varphi})\to QxP_{\varphi}(\vec z_{\varphi})\}\cup \{\forall x\psi\:|\:\psi\in\mathcal S^+(\varphi)\}$\\$\mathcal S^-(Qx\varphi(x))  = \{QxP_{\varphi}(\vec z_{\varphi})\to P_{Qx\varphi}(\vec z_{Qx\varphi})\}\cup \{\forall x\psi\:|\:\psi\in\mathcal S^-(\varphi)\}$
	\end{itemize}
	and have $\mathcal S(\varphi) = \mathcal S^+(\varphi)\cup\mathcal S^-(\varphi)$.
\end{definition}

@@

\begin{definition}
	For every classical and intuitionistic structure $\mathcal M$ define a structure $\mathcal S(\mathcal M,\varphi)$ that agrees with $\mathcal M$ on everything except the interpretation(s) of atoms of the form $P_\psi$. By slight abuse of notation we denote with $\vec z_\psi$ elements of the domain instead of variables. In the classical case have
	$$P_A^I(\vec z_A):\Leftrightarrow A^I(\vec z_A)$$
	and
	$$P_{\varphi\wedge\psi}^I(\vec z_{\varphi\wedge\psi}) :\Leftrightarrow P_{\varphi}^I(\vec z_\varphi)\wedge P_{\psi}^I(\vec z_\psi)\indent P_{\varphi\vee\psi}^I(\vec z_{\varphi\vee\psi}) :\Leftrightarrow P_{\varphi}^I(\vec z_\varphi)\vee P_{\psi}^I((\vec z_\psi))$$$$ P_{\varphi\to\psi}^I(\vec z_{\varphi\to\psi}) :\Leftrightarrow (\neg P_{\varphi}^I(\vec z_{\varphi}))\vee P_{\psi}^I(\vec z_{\psi})$$
	$$P_{\forall x\varphi}^I(\vec z_{\forall x\varphi}) :\Leftrightarrow \{\vec z\:|\:\:P_{\varphi}^I(\vec z_\varphi) \text{ for all $x\in M$}\}$$$$ P_{\exists x\varphi}^I(\vec z_{\exists x\varphi}) :\Leftrightarrow \{\vec z\:|\:\:P_{\varphi}^I(\vec z_\varphi) \text{ for some $x\in M$}\}$$
	\\
	and for intuitionistic logic and some world $u$
	$$P_A^{I_u}(\vec z_A):\Leftrightarrow A^{I_u}(\vec z_A)$$
	and
	$$P_{\varphi\wedge\psi}^{I_u}(\vec z_{\varphi\wedge\psi}) :\Leftrightarrow P_{\varphi}^{I_u}(\vec z_\varphi)\wedge P_{\psi}^{I_u}(\vec z_\psi)\indent P_{\varphi\vee\psi}^{I_u}(\vec z_{\varphi\vee\psi}) :\Leftrightarrow P_{\varphi}^{I_u}(\vec z_\varphi)\vee P_{\psi}^{I_u}((\vec z_\psi))$$$$ P_{\varphi\to\psi}^{I_u}(\vec z_{\varphi\to\psi}) :\Leftrightarrow(\neg P_{\varphi}^{I_w}(\vec z_{\varphi}))\vee P_{\psi}^{I_w}(\vec z_{\psi})\text{ for all $w\geq u$}$$
	$$P_{\forall x\varphi}^{I_u}(\vec z_{\forall x\varphi}) :\Leftrightarrow P_{\varphi}^{I_w}(\vec z_\varphi) \text{ for all $w\geq u$, $x\in M_w$}$$$$ P_{\exists x\varphi}^{I_u}(\vec z_{\exists x\varphi}) :\Leftrightarrow P_{\varphi}^{I_u}(\vec z_\varphi) \text{ for some $x\in M_u$}$$
	\\
\end{definition}
